
---
# title: "DATA 607 WEEK 7 ASSIGNMENT <br /> WORKING WITH HTML, XML AND JSON IN R"
# author: "[Kleber Perez - `r format(Sys.Date(), '%B %d, %Y')`](https://www.linkedin.com/in/kleberperez/)"
output: 
  html_document:
    #code_folding: show
    theme:  sandstone
    highlight: pygments
    css: ./w7css.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# 1. Library
library(kableExtra)
library(rvest)
library(dplyr)
library(XML)
library(RCurl)
library(rjson)
library(RJSONIO)
library(jsonlite)

```

<div class="jumbotron jumbotron-fluid">
  <div class="btn btn-default btn-block">
  <br />
  
  <p class="lead">DATA 607 WEEK 7 ASSIGNMENT <br />WORKING WITH HTML, XML AND JSON IN R <br />[`r format(Sys.Date(), '%B %d, %Y')`](https://www.linkedin.com/in/kleberperez/) </p>

  <p class="lead">SOURCE FILES, R SCRIPTS AND RMARKDOWN ON GITHUB </p>

  <a class="label label-success" href="https://www.linkedin.com/in/kleberperez/" target="_blank" role="button">KLEBER PEREZ</a> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;
  <a class="label label-success" href="http://rpubs.com/kleberperez/477939" role="button">RPUBS</a>
  <a class="label label-success" href="https://github.com/kleberperez1/CUNY-SPS-Data607-Project3" role="button">GITHUB</a>

  <br />
  
  </div>
</div>


# <span id="maintop">Favorite books and subjects!</span> {.tabset .tabset-dropdown}

## Please make a selection to continue..

## <span id="gotohtml">HTML books</span> 

<div class="jumbotron jumbotron-fluid">

## Reading HTML Table Format

<div class="alert alert-info" role="alert">
An HTML table format is defined with the <span class="label label-info badge">&nbsp; &lt;table&gt; &nbsp;</span> tag.
Each table row is defined with the <span class="label label-info badge">&nbsp; &lt;tr&gt; &nbsp;</span> tag. A table header is defined with the <span class="label label-info badge">&nbsp; &lt;th&gt; &nbsp;</span> tag. By default, table headings are bold and centered. A table data/cell is defined with the <span class="label label-info badge">&nbsp; &lt;td&gt; &nbsp;</span> tag.
</div> 
</div>

<div class="jumbotron jumbotron-fluid">

```{r}
# html variable in R 
url_html <- read_html("https://raw.githubusercontent.com/kleberperez1/CUNY-SPS-Data607-Week7-Assignment/master/books.html")

tabs <- url_html %>%
  html_nodes("table") %>%
  html_table(fill = TRUE)
html_frame <- tabs[[1]]

kable(html_frame) %>%
  kable_styling(bootstrap_options = "striped", font_size = 10) %>%
  scroll_box()

```

<br />

</div>

<a href="#maintop">Go to top</a>

<br />

## <span id="gotoxml">XML books &nbsp;</span> 

<div class="jumbotron jumbotron-fluid">

## Reading XML File Format

<div class="alert alert-info" role="alert">

<span class="label label-info badge">XML</span> is a file extension for an Extensible Markup Language (<span class="label label-info badge">XML</span>) file format used to create common information formats and share both the format and the data on the World Wide Web, intranets, and elsewhere using standard ASCII text. <span class="label label-info badge">XML</span> is similar to <span class="label label-info badge">HTML</span>.

</div> 
</div>

<div class="jumbotron jumbotron-fluid">

```{r df}
xmlfile<-getURL("https://raw.githubusercontent.com/kleberperez1/CUNY-SPS-Data607-Week7-Assignment/master/books.xml")
xmlBooks<-tbl_df(xmlToDataFrame(xmlfile))

xmlBooks %>% kable() %>% kable_styling(bootstrap_options = "striped", font_size = 10) %>% scroll_box()

```

<br />

</div>


<a href="#maintop">Go to top</a>

<br />


## <span id="gotojson">JSON books</span> 

<div class="jumbotron jumbotron-fluid">

## Reading JSON Syntax

<div class="alert alert-info" role="alert">

The <span class="label label-info badge">JSON</span> syntax is a subset of the <span class="label label-info badge">JavaScript</span> syntax. <br />
<span class="label label-info badge">JSON</span> data is written as name/value pairs. <br />
A name/value pair consists of a field name (in double quotes), followed by a colon, followed by a value:
<span class="label label-info badge">"name":"John"</span>.

</div> 
</div>

<div class="jumbotron jumbotron-fluid">

```{r}
jsonFile<-"https://raw.githubusercontent.com/kleberperez1/CUNY-SPS-Data607-Week7-Assignment/master/books.json"
isValidJSON(jsonFile)

jsonbooks<-tbl_df(as.data.frame(fromJSON(jsonFile)))
jsonbooks %>% kable() %>% kable_styling(bootstrap_options = "striped", font_size = 10) %>% scroll_box()

```

<br />

</div>

<a href="#maintop">Go to top</a>

<br />


## <span id="gotoconclusion">Conclusion</span> 

<div class="jumbotron jumbotron-fluid">

## Conclusion

<div class="alert alert-info" role="alert">

  <span class="label label-default">Are the three data frames identical? </span> <br />
  <span class="label label-info">The three data frames are not the identical. The data size for the three files are different.<br />The <span class="label label-info badge">HTML</span> data frame is the largest of all, followed by the <span class="label label-info badge">JSON</span> data frame and lastly <br />the <span class="label label-info badge">XML</span> data frame is the smallest in size.</span>

</div>
</div> 

<div class="jumbotron jumbotron-fluid">
  <div class="btn btn-default btn-block">

  <p class="lead">SOURCE FILES, R SCRIPTS AND RMARKDOWN ON GITHUB </p>
  <a class="label label-success" href="http://rpubs.com/kleberperez/477939" role="button">RPUBS</a>
  <a class="label label-success" href="https://github.com/kleberperez1/CUNY-SPS-Data607-Project3" role="button">GITHUB</a>

  </div>
</div>

<a href="#maintop">Go to top</a>

</div>

# &nbsp;

<br />

* * *


> *Please email to: * <a href="mailto:kleber.perez@live.com">Kleber Perez</a> *for any suggestion.*

<footer class="border-top text-muted fixed-bottom">

        DATA 607 Week 7 Assignment - MSDS 2019 Program.

</footer>

\textbf{Text ignored: END of other links}

<br />
<br />
<br />
<br />


